QALY Comparison - Living Wage Intervention

### 2023-11-14 minos/testing/QALY_comparison_energyCrises.Rmd
Attempting to fix weird bug where PCS doesnt transition. Think this will fix it. Updated some paths in config/uk_scaled.yaml, updated some functions in minos/utils_qaly.R and some tweaks to the QALY comparison scripts

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')

>>>>

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'SF12_uk_scaled')

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Attempting to fix weird bug where PCS doesnt transition. Think this will fix it. Updated some paths in config/uk_scaled.yaml, updated some functions in minos/utils_qaly.R and some tweaks to the QALY comparison scripts

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'default_config')

@@

@@

```{r}
cost.per.qaly(base = noSupport,
              base.name = 'energyDownliftNoSupport',
              int = support,
              int.name = 'energyDownlift',
              QALY_value = 60000)  # QALY value == £60,000
```

@@

```{r}
ICER(base = noSupport,
     base.name = 'energyDownliftNoSupport',
     int = support,
     int.name = 'energyDownlift',
     QALY_value = 60000)
```

>>>>

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'SF12_uk_scaled')

@@

```{r}
# base <- noSupport
# base.name <- 'energyDownliftNoSupport'
# int <- support
# int.name <- 'energyDownlift'
# 
# combined <- rbind(base, int)
# 
# ## now SF12 plots for comparison
# p1 <- ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_smooth()
# p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_smooth()
# 
# print(p1)
# print(p2)
# 
# combined.SF12 <- combined %>%
#   select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%
#   pivot_wider(names_from = 'intervention',
#               values_from = c('SF_12_MCS', 'SF_12_PCS')) %>%
#   mutate(MCS_diff = .data[[paste0('SF_12_MCS_', int.name)]] - .data[[paste0('SF_12_MCS_', base.name)]],
#          PCS_diff = .data[[paste0('SF_12_PCS_', int.name)]] - .data[[paste0('SF_12_PCS_', base.name)]]) %>%
#   select(run_id, year, MCS_diff, PCS_diff)
# 
# p3 <- ggplot(combined.SF12, aes(x = year, y = MCS_diff)) +
#   geom_smooth() +
#   geom_hline(yintercept = 0, linetype = 'dashed') +
#   labs(title = 'Change in SF_12_MCS', subtitle = paste0(int.name, ' vs ', base.name)) +
#   xlab('Year') +
#   ylab('Change in MCS')
# 
# p4 <- ggplot(combined.SF12, aes(x = year, y = PCS_diff)) +
#   geom_smooth() +
#   geom_hline(yintercept = 0, linetype = 'dashed') +
#   labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
#   xlab('Year') +
#   ylab('Change in MCS')
# 
# print(p3)
# print(p4)

@@

```{r}
cost.per.qaly(base = noSupport,
              base.name = 'energyDownliftNoSupport',
              int = support,
              int.name = 'energyDownlift',
              QALY_value = 60000,  # QALY value == £60,000
              int.label <- 'EPCG')
```

@@

```{r}
ICER(base = noSupport,
     base.name = 'energyDownliftNoSupport',
     int = support,
     int.name = 'energyDownlift',
     QALY_value = 60000,
     int.label = 'EPCG')
```

```{r}
#ICER <- function(base, base.name, int, int.name, QALY_value) {

base <- noSupport
base.name <- 'energyDownliftNoSupport'
int <- support
int.name <- 'energyDownlift'
QALY_value <- 60000

combined <- rbind(base, int)

combined.cost.mean <- combined %>%
  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * QALY_value) %>%
  group_by(run_id, year, intervention) %>%
  summarise(across(everything(), mean))

# ICER = (C1 - C0) / (E1 - E0)
# where
# C1 = cost of intervention
# E1 = effect of intervention
# C0 = cost of control group
# E0 = effect of control group

# prepare var names
c1 <- paste('total_boost', int.name, sep='_')
c0 <- paste('total_boost', base.name, sep='_')
e1 <- paste('QALYs', int.name, sep='_')
e0 <- paste('QALYs', base.name, sep='_')

ICER <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER = (.data[[c1]] - .data[[c0]]) / (.data[[e1]] - .data[[e0]])) %>%
  select(run_id, year, ICER) %>%
  mutate(intervention = int.name)

pc1 <- quantile(ICER$ICER, .01)
print(pc1)
print(min(ICER$ICER))
pc99 <- quantile(ICER$ICER, .99)
print(pc99)
print(max(ICER$ICER))

ICER <- filter(ICER, ICER < pc99, ICER > pc1)
print(min(ICER$ICER))
print(max(ICER$ICER))

p1 <- ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name))
print(p1)

ICER.final <- ICER %>%
  group_by(run_id, intervention) %>%
  summarise(ICER = mean(ICER)) %>%
  group_by(intervention) %>%
  summarise(margin = (qt(0.975, df=n() - 1) * sd(ICER)) / sqrt(n()),
            ICER = mean(ICER))

p2 <- ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = ICER - margin, ymax = ICER + margin, width = 0.4, group = intervention)) +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name)) +
  xlab('Intervention')
print(p2)

print(paste0('ICER == ', ICER.final$ICER, ' +- ', ICER.final$margin))
```

### 2023-11-14 minos/testing/QALY_comparison_livingWage.Rmd
Attempting to fix weird bug where PCS doesnt transition. Think this will fix it. Updated some paths in config/uk_scaled.yaml, updated some functions in minos/utils_qaly.R and some tweaks to the QALY comparison scripts

```{r}
cost.per.qaly(base = base,
              base.name = 'baseline',
              int = wage,
              int.name = 'livingWageIntervention',
              QALY_value = 60000)  # QALY value == £60,000
```

@@

```{r}
ICER(base = base,
     base.name = 'baseline',
     int = wage,
     int.name = 'livingWageIntervention',
     QALY_value = 60000)
```

>>>>

```{r}
cost.per.qaly(base = base,
              base.name = 'baseline',
              int = wage,
              int.name = 'livingWageIntervention',
              QALY_value = 60000,
              int.label <- 'LivingWage')  # QALY value == £60,000
```

@@

```{r}
ICER(base = base,
     base.name = 'baseline',
     int = wage,
     int.name = 'livingWageIntervention',
     QALY_value = 60000,
     int.label = 'LivingWage')
```

```{r}
#ICER <- function(base, base.name, int, int.name, QALY_value) {

base <- base
base.name <- 'baseline'
int <- wage
int.name <- 'livingWageIntervention'
QALY_value <- 60000
int.label <- 'LivingWage'

combined <- rbind(base, int)

combined.cost.mean <- combined %>%
  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * QALY_value) %>%
  group_by(run_id, year, intervention) %>%
  summarise(across(everything(), mean))

# ICER = (C1 - C0) / (E1 - E0)
# where
# C1 = cost of intervention
# E1 = effect of intervention
# C0 = cost of control group
# E0 = effect of control group

# prepare var names
c1 <- paste('total_boost', int.name, sep='_')
c0 <- paste('total_boost', base.name, sep='_')
e1 <- paste('QALYs', int.name, sep='_')
e0 <- paste('QALYs', base.name, sep='_')

ICER <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER = (.data[[c1]] - .data[[c0]]) / (.data[[e1]] - .data[[e0]])) %>%
  select(run_id, year, ICER) %>%
  mutate(intervention = int.label)

pc1 <- quantile(ICER$ICER, .01)
print(pc1)
print(min(ICER$ICER))
pc99 <- quantile(ICER$ICER, .99)
print(pc99)
print(max(ICER$ICER))

ICER <- filter(ICER, ICER < pc99, ICER > pc1)
print(min(ICER$ICER))
print(max(ICER$ICER))

p1 <- ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name))
print(p1)

ICER.final <- ICER %>%
  group_by(run_id, intervention) %>%
  summarise(ICER = mean(ICER)) %>%
  group_by(intervention) %>%
  summarise(margin = (qt(0.975, df=n() - 1) * sd(ICER)) / sqrt(n()),
            ICER = mean(ICER))

p2 <- ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = ICER - margin, ymax = ICER + margin, width = 0.4, group = intervention)) +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name)) +
  xlab('Intervention')
print(p2)

print(paste0('ICER == ', ICER.final$ICER, ' +- ', ICER.final$margin))
```
